DRAFT: Harmonized and trait aggregation paper

### 2020-10-21 Paper/Draft_harmonization_paper.tex
21.10: Improved writing sim method section

To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we simulated three different taxonomic hierarchies. 
1) A family with an equal number of genera and species (5 genera each with 5 species respectively) 
% denoted as \textit{equal scenario}.
2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively). 
3) A family where all genera have a different number of species (8, 2, 7, 3, 5).
Every simulated taxonomic hierarchy was assigned a hypothetical grouping feature with 3 traits. The affinities for each trait were sampled from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviation (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability. The truncated normal distribution was bound to 0 and 1. The traits were normalized so that they sum up to one for each species, similar to the data processing of the trait databases. 100 Simulations for each standard deviation were carried out. Hence, 500 simulations were run for each simulation scenario (in total 1500). All trait aggregation methods were applied to each simulated dataset and the results were compared.

>>>>

To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we created three hypothetical examples of different taxonomic hierarchies. 
1) A family with an equal number of genera and species (5 genera each with 5 species respectively) 
% denoted as \textit{equal scenario}.
2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively). 
3) A family where all genera have a different number of species (8, 2, 7, 3, 5). Every hypothetical taxonomic hierarchy was assigned a hypothetical grouping feature with 3 traits. The affinities for each trait were simulated by sampling from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviation (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability. The truncated normal distribution was bound to 0 and 1. The traits were normalized so that they sum up to one for each species, similar to the data processing of the trait databases. 100 Simulations for each standard deviation were carried out. Hence, 500 simulations were run for each simulation scenario (in total 1500). All trait aggregation methods were applied to each simulated dataset and the results were compared.

### 2020-10-21 Paper/Results/SI.tex
21.10: Started results simulation
21.10: Improved writing sim method section

\subsection*{Comparison of the trait aggregation methods with each other}
\label{sec:compa_aggr_methods}

@@

% \subsection*{Differences in trait affinities obtained by trait aggregation methods compared to traits assigned at family-level}
%? Cases where trait affinities aggregated through \textit{direct\_agg} differed more than 60 \% from trait affinities assigned at family-level by Chessman 2017

>>>>

\subsection*{Differences in trait affinities obtained by trait aggregation methods com-pared to traits assigned at family-level}

\subsubsection*{Comparison of the trait aggregation methods with each other}
\label{sec:compa_aggr_methods}

@@

\subsubsection*{Simulation of varying taxonomic hierarchies}

\begin{figure}[H]
    \centering
    \includegraphics[width=16.5cm, height=10cm]{Overview_sim_results.png}
    \caption{Ranges of aggregated trait affinities for the three scenarios and simulated levels of trait variability. Each scenario encompasses a family with 25 species with a different taxonomic hierarchy. Boxplots depict aggregated trait affinities of 100 runs for every trait aggregation method. T1 to T3 are the simulated traits.}
    \label{fig:overview_sim_results}
\end{figure}
